Tabular Constraint Learning

### 2016-04-08 Paper/ECAI/tabular.tex
writing the paper

\newcommand{\constraints}{\ensuremath{\mathcal{C}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateAssignments}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findSolutions}}
\newcommand{\postprocess}{\format{pruneRedundant}}

\newcommand{\CName}{Name\xspace}
\newcommand{\CSignature}{Signature\xspace}
\newcommand{\CFunction}{Function\xspace}
\newcommand{\dependecies}{\ensuremath{\mathcal{D}}\xspace}
\newcommand{\groups}{\ensuremath{\mathcal{G}}\xspace}

@@

\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $G$ -- set of groups
    \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignments
    \State $S \gets \emptyset$ \Comment{The set of solutions}
  \For{$c \in \constraints$} \Comment{\constraints -- partially ordered set of Excel constraints; Table \ref{table:constraints}}
  \State $v_1, ..., v_n =$ variables of $c$ 
    \For{$v_1{:}~G_1, \dots, v_n{:}~G_n \in \generategroups(c, G, S)$}
      \State $S \gets S \cup \findassignment(c, v_1{:}~G_1, \dots, v_n{:}~G_n, S)$
    \EndFor
  \EndFor\\
\Return $S$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}
\subsection{Groups, Type-consistency and Constraints}
In this work we distinguish the following types of data: numeric and textual. The numeric type has two subtypes: integers and floats. We also consider the special element called \textit{None}, which has two types: numeric and textual. A set is called \textit{type-consistent} iff all elements are either numeric or textual. Certain constraints, such as \textit{rank} or \textit{series}, make use of the numeric sub-types by requiring its arguments to be integers.

@@

\begin{framed}
  \begin{tabular}{ll}

    \multicolumn{2}{c}{{\textbf{Tabular Constraint Learning Problem}}}\\
    &\\
    \textbf{Given:} & The set of all groups $\groups$ and the set of Excel  \\
    \phantom{Given:} & constraints $\constraints$ with its dependencies DAG $\dependecies$\\
    \textbf{Find: } & text
  \end{tabular}
\end{framed}

\section{Approach to Tabular Constraint Learning}
Let us describe the key steps and functions in Algorithm \ref{algo:tcl}. Essentially, the algorithm has two steps: candidate group generation and subgroup satisfaction search, which is in line with the ``generate-and-test'' paradigm that is well-known in AI \cite{whaisasp}. Let us elaborate on each step in detail.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.20\textwidth]{figures/constraint_dependency.png}
  \caption{Constraint Learning Order. The \textcolor{green}{solid} arrows indicate a construction order, i.e., learning one constraint is necessary to build the other. The \textcolor{red}{dashed} arrows indicate a pruning order, the former constraint is used to prune the latter.}
  \label{fig:learning_order}
\end{figure}

@@

\subsection{Workflow}
\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $D$ -- dataset, (optional: tables $T$, groups $G$)
    \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignment
    \If{$T$ is \textbf{not} provided}
      \State $T \gets \extracttables(D)$
    \EndIf
    \If{$G$ is \textbf{not} provided}
      \State $G \gets \extractgroups(D, T)$
    \EndIf
    \State $S \gets \learnconstraints(G)$
    \State $S \gets \postprocess(S)$
    \State \Return $S$
\end{algorithmic}
\caption{Workflow}
\label{algo:workflow}
\end{algorithm}

>>>>

\newcommand{\constraints}{\ensuremath{\mathcal{C}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateAssignments}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findSolutions}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{orderedConstraints}}

\newcommand{\CName}{Name\xspace}
\newcommand{\CSignature}{Signature\xspace}
\newcommand{\CFunction}{Function\xspace}
\newcommand{\dependencies}{\ensuremath{\mathcal{D}}\xspace}
\newcommand{\groups}{\ensuremath{\mathcal{G}}\xspace}

@@

\subsection{Groups, Type-consistency and Constraints}
In this work we distinguish the following types of data: numeric and textual. The numeric type has two subtypes: integers and floats. We also consider the special element called \textit{None}, which has two types: numeric and textual. A set is called \textit{type-consistent} iff all elements are either numeric or textual. Certain constraints, such as \textit{rank} or \textit{series}, make use of the numeric sub-types by requiring its arguments to be integers.

@@

\begin{minipage}[c]{14em}
  \vspace{5pt}
  \begin{tabular}{ll}
    \multicolumn{2}{l}{{\textbf{Tabular Constraint Learning Problem}}}\\
    \vspace{-4pt}
    &\\
    \textbf{Given:}& the set of all groups $\groups$ and of Excel constraints $\constraints$\\
    \textbf{Find:}& for each constraint  $c$ in \constraints all the subgroups of $\groups$\\ 
    & satisfying the \CSignature and \CFunction of $c$ 
  \end{tabular}
\end{minipage}

\section{Approach to Tabular Constraint Learning}
\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $\constraints$ -- Excel constraints, \dependencies -- dependency graph 
    \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignments
    \State $S \gets \emptyset$ \Comment{The set of solutions}
  \For{$c \in \constrainttorder(\constraints,\dependencies)$} 
  \State $v_1, ..., v_n =$ variables of $c$ 
    \For{$v_1{:}~G_1, \dots, v_n{:}~G_n \in \generategroups(c, G, S)$}
      \State $S \gets S \cup \findassignment(c, v_1{:}~G_1, \dots, v_n{:}~G_n, S)$
    \EndFor
  \EndFor\\
\Return $S$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}

Let us describe the key steps and functions in Algorithm \ref{algo:tcl}. Essentially, the algorithm has three steps: constraint ordering, candidate group generation and subgroup satisfaction search, which is in line with the ``generate-and-test'' paradigm that is well-known in AI \cite{whaisasp}. Let us elaborate on each step in detail.

\paragraph{Constraint ordering} $\constrainttorder(\constraints,\dependencies)$ \sergey{explaination that solutions to certain constraints allows us to prune solutions to other constraints -- subsumption, condensed representation}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.20\textwidth]{figures/constraint_dependency.png}
  \caption{Constraint Learning Order. The \textcolor{green}{solid} arrows indicate a construction order, i.e., learning one constraint is necessary to build the other. The \textcolor{red}{dashed} arrows indicate a subsumption order, the former constraint is used to prune the latter.}
  \label{fig:learning_order}
\end{figure}

@@

\subsection{Workflow}
\begin{algorithm}[thb]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $D$ -- dataset, \constraints -- constraints, \dependencies -- dependencies \\(optional: tables $T$, groups $G$)
    \State \textbf{Output:} $S$ -- learned constraints with their satisfaction assignment
    \If{$T$ is \textbf{not} provided}
      \State $T \gets \extracttables(D)$
    \EndIf
    \If{$G$ is \textbf{not} provided}
      \State $G \gets \extractgroups(D, T)$
    \EndIf
    \State $S \gets \learnconstraints(G,\constraints,\dependencies)$
    \State $S \gets \postprocess(S)$
    \State \Return $S$
\end{algorithmic}
\caption{Workflow}
\label{algo:workflow}
\end{algorithm}
